Motion Planning and Robust Fault-Tolerant Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-11-25 paper/paper.tex
ieeetr->IEEEtran, change http://

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
\begin{equation}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r$ through (6). Since there is a complex coordinate transformation between $q_r$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model. Although there exist a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

@@

% \nocite{*}
\bibliographystyle{ieeetr}
\bibliography{citation}
% \begin{thebibliography}{00}
%     \bibitem{9700861} L. Kloeker, T. Moers, L. Vater, A. Zlocki, and L. Eckstein, “Utilization
%     and potentials of unmanned aerial vehicles (uavs) in the field of automated
%     driving: A survey,” in 2021 5th International Conference on Vision, Image
%     and Signal Processing (ICVISP), pp. 9–17, 2021
% \end{thebibliography}

>>>>

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in $\widehat{Y_b}$ direction as the same form):
\begin{equation} \label{eq:x_zmp}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular velocity component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}). Since there is a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls on the support polygon but the support polygon also has a relationship with $q_r(t)$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. It is to find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of actual robot dynamic model. Although there exist a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

@@

% \nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{citation}
% \begin{thebibliography}{00}
%     \bibitem{9700861} L. Kloeker, T. Moers, L. Vater, A. Zlocki, and L. Eckstein, “Utilization
%     and potentials of unmanned aerial vehicles (uavs) in the field of automated
%     driving: A survey,” in 2021 5th International Conference on Vision, Image
%     and Signal Processing (ICVISP), pp. 9–17, 2021
% \end{thebibliography}
